### 2015-03-02 fundamentals/impl.tex
addresses the comment from Erich ' it feels like the APIs are important and more should be said about them.  Specifically to communicate to readers that Cyclus makes it easy to pass needed information from/to the rest of the simulation, and that the possible classes of needed information have been anticipated.'

\Cyclus achieves this behavior by implementing its generic \gls{API} and
modular architecture via a suite of dynamically loadable plug-in libraries as
pictured in Figure \ref{fig:framework}.
Though common in modern software architecture, such a plug-in paradigm has not
previously been implemented in a nuclear fuel cycle simulator. Dynamically
loadable libraries are the primary mechanism for extending \Cyclus' capability.
The core framework operates
independently from the plug-in libraries, and the APIs are designed to provide archetype developers with the tools needed to collect inputs required by their archetype as well as return outputs. Hence the libraries enable customization and extension of \Cyclus' capabilities independent of the core.

>>>>

\Cyclus achieves this behavior by implementing generic \glspl{API} and a
modular architecture via a suite of dynamically loadable plug-in libraries
(pictured in Figure \ref{fig:framework}). By anticipating the possible classes of
information required by the simulation kernel, the \Cyclus \glspl{API}
facilitate information passing between the plug-in agents and the core
framework.
Though common in modern software architecture, such a plug-in paradigm has not
previously been implemented in a nuclear fuel cycle simulator.
It allows the core \Cyclus framework to operate independently from the plug-in libraries, and the
dynamically loadable plug-ins to be the primary mechanism for extending \Cyclus'
capabilities independent of the core.
